---
title: "Project Assignment"
author: "Niccolo Tosi"
date: "04 dicembre 2016"
output: html_document
---

This document is a draft. 

INPUT DATA:

Input data consist of a set of time series corresponding to different sessions of Unilateral Dumbbell Biceps Curl which have been done in five different fashions (classe): {A,B,C,D,E}. Training and test sets are provided. 

A few variables in the training set are not present in the test set.

In total, 19622 records with 160 features are included in the training set. All the average values present NA. Only 406 records are complete.

Each time series is identified by a different num_window variable. Six different users performed the test.

OBJECTIVE:

The objective is to train a predictor in order to identify the "classe". 



```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
